### 2018-11-09 Sections/about_the_authors.tex
Resized figs for 1 column
braket

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney, Australia (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 50 publications and 1,300+ citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded \textsc{BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

@@

%
% Ryan Mann
%

%\begin{center}
%\includegraphics[clip=true, width=0.475\textwidth]{photo_ryan_mann}
%\end{center}

%Ryan Mann is a PhD candidate in the Centre for Quantum Software \& Information at the University of Technology Sydney. He is a better rock-climber than he is physicist, despite being outstanding at the latter.

%\comment{Complete this section}

>>>>

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney, Australia (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 50 publications and 1,500+ citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded \textsc{BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

@@

### 2018-11-09 Sections/collision_handling_and_classical_errors.tex
braket

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem\index{No-cloning theorem}\footnote{The no-cloning theorem states that it is impossible to take a completely general, unknown quantum state and prepare an identical copy of it. That is, there is no quantum process\index{Quantum processes} implementing the map \mbox{$\mathcal{E}(\hat\rho\otimes\ket{0}\bra{0}) \to \hat\rho\otimes\hat\rho$} for unknown $\hat\rho$. Note that this result applies when $\hat\rho$ is arbitrary and unknown, but in general needn't apply if restricted to a particular basis, subject to other constraints, or we have \textit{a priori} knowledge of the state. \textit{Proof}:\index{No-cloning theorem!Proof} To see this, consider the unitary evolution \mbox{$\hat{U}\ket\psi\ket{e} = e^{i\alpha(\psi,e)}\ket\psi\ket\psi$}, for some normalised ancillary state $\ket{e}$, where $\alpha$ denotes an irrelevant global phase factor. We have \mbox{$\langle\psi|\phi\rangle\langle e|e\rangle = \bra\psi\bra{e}\hat{U}^\dag\hat{U}\ket{\phi}\ket{e} = e^{-i[\alpha(\psi,e)-\alpha(\phi,e)]} \langle\psi|\phi\rangle^2$}. Since $\ket{e}$ is normalised, this implies \mbox{$|\langle\psi|\phi\rangle| = |\langle\psi|\phi\rangle|^2$}, which can only be true if \mbox{$ |\langle\psi|\phi\rangle|=0$} or \mbox{$ |\langle\psi|\phi\rangle|=1$}, which does not hold in general for arbitrary states $\ket\psi$ and $\ket\phi$. However, clearly if $\ket\psi$ and $\ket\phi$ are restricted to being equal or orthogonal then this constraint can be satisfied with an appropriate choice of $\hat{U}$, since this corresponds to classical cloning\index{Classical cloning}. This proof applies to unitary evolution. What about generic quantum processes? In that case we merely need to assume that the ancillary state $\ket{e}$ acts on a joint primary/environment system, and the same argument applies.} implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

>>>>

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem\index{No-cloning theorem}\footnote{The no-cloning theorem states that it is impossible to take a completely general, unknown quantum state and prepare an identical copy of it. That is, there is no quantum process\index{Quantum processes} implementing the map \mbox{$\mathcal{E}(\hat\rho\otimes\ket{0}\bra{0}) \to \hat\rho\otimes\hat\rho$} for unknown $\hat\rho$. Note that this result applies when $\hat\rho$ is arbitrary and unknown, but in general needn't apply if restricted to a particular basis, subject to other constraints, or we have \textit{a priori} knowledge of the state. \textit{Proof}:\index{No-cloning theorem!Proof} To see this, consider the unitary evolution \mbox{$\hat{U}\ket\psi\ket{e} = e^{i\alpha(\psi,e)}\ket\psi\ket\psi$}, for some normalised ancillary state $\ket{e}$, where $\alpha$ denotes an irrelevant global phase factor. We have \mbox{$\braket{\psi|\phi}\braket{e|e} = \bra\psi\bra{e}\hat{U}^\dag\hat{U}\ket{\phi}\ket{e} = e^{-i[\alpha(\psi,e)-\alpha(\phi,e)]} \braket{\psi|\phi}^2$}. Since $\ket{e}$ is normalised, this implies \mbox{$|\braket{\psi|\phi}| = |\braket{\psi|\phi}|^2$}, which can only be true if \mbox{$ |\braket{\psi|\phi}|=0$} or \mbox{$ |\braket{\psi|\phi}|=1$}, which does not hold in general for arbitrary states $\ket\psi$ and $\ket\phi$. However, clearly if $\ket\psi$ and $\ket\phi$ are restricted to being equal or orthogonal then this constraint can be satisfied with an appropriate choice of $\hat{U}$, since this corresponds to classical cloning\index{Classical cloning}. This proof applies to unitary evolution. What about generic quantum processes? In that case we merely need to assume that the ancillary state $\ket{e}$ acts on a joint primary/environment system, and the same argument applies.} implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.
